### 2009-08-10 doc/manuals/user_interface/ui-data.tex
Starting cleaning up documentation
clean up arcls/cp/rm doc

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcls [options] $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-l} &  & detailed listing\\
    \texttt{-L} &  & detailed listing including URLs from which file can 
    be downloaded and\\ & & temporary cached locations\\
    Arguments:&&\\
    \texttt{URL} && file or directory URL\\
\end{longtable}

@@

\begin{verbatim}
    ngls rls://rc.host:38203/logical_file_name
    ngls -l gsiftp://lscf.nbi.dk:2811/jobs/1323842831451666535
    ngls -L srm://grid.uio.no:58000/srm/managerv1/johndoe/log2
\end{verbatim}

@@

The \texttt{arccp}\footnote{In ARC $\leq$ 0.5.28 was called
  \texttt{ngcopy}} \index{arccp}\index{commands:arccp} is a powerful
tool to copy files over the Grid. It is a part of the Grid Manager,
but can be used by the User Interface as well.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccp [options] $<$source$>$ $<$destination$>$}
\end{shaded}
\versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level: from -3 = quiet to 3 = verbose\\
    \texttt{-y} & \textit{cache\_path} & path to local cache (use to put file into cache)\\
    \texttt{-Y} & \textit{cache\_data\_path} & path for cache data (if different from -y)\\
    \texttt{-p} && use passive transfer (does not work if secure is on, default if secure is not requested)\\
    \texttt{-n} && do not try to force passive transfer\\
    \texttt{-i} && show progress indicator\\
    \texttt{-u} && use secure transfer (insecure by default)\\
    \texttt{-r} & \textit{recursion\_level} & operate recursively (if possible) up to specified level (0 - no recursion)\\
    \texttt{-R} & \textit{number} & how many times to retry transfer of every file before failing\\
    \texttt{-t} & \textit{time} & timeout in seconds (default 20)\\
    \texttt{-f} && if the destination is an indexing service and not the same as the source and the destination is already registered, then the copy is normally not done. However, if this option is specified the source is assumed to be a replica of the destination created in an uncontrolled way and the copy is done like in case of replication\\
    \texttt{-T} && do not transfer file, just register it - destination must be non-existing meta-url\\
    Arguments:&&\\
    \texttt{source} && source URL\\
    \texttt{destination} && destination URL\\
\end{longtable}

@@

\begin{framed}
   Since the job ID is in fact a \verb#gsiftp://# URL of the job
   top directory, you can use \texttt{arccp} to copy files from the
   job directory at any time.
\end{framed}

@@

\begin{verbatim}
    ngcp gsiftp://lscf.nbi.dk:2811/jobs/1323842831451666535/job.out \
              file:///home/myname/job2.out
    ngcp gsiftp://aftpexp.bnl.gov;threads=10/rep/my.file \
              rc://;threads=4@grid.uio.no/lc=Collection,rc=Catalog/zebra4.f
    ngcp http://www.nordugrid.org/data/somefile gsiftp://hathi.hep.lu.se/data/
\end{verbatim}

@@

The \texttt{arcrm}\footnote{In ARC $\leq$ 0.5.28 was called
  \texttt{arcremove}} \index{arcrm}\index{commands:arcrm}
command allows users to erase files at any location specified by a
valid URL.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{ngrm [options] $<$source$>$}
\end{shaded}
\versions{ARC 0.3, ARC 0.4, ARC 0.5, ARC 0.6}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-c} & &continue with meta-data even if it failed to delete real file\\
    \texttt{-C} & \textit{cache\_data\_path} & store cached data\\
    Arguments:&&\\
    \texttt{source} && source URL\\
\end{longtable}

\begin{framed}
   A convenient use for \texttt{ngarc} is to erase the files in a data
   indexing catalog (RC, RLS or such), as it will not only remove the
   physical instance, but also will clean up the database record.
\end{framed}

@@

\begin{verbatim}
    ngrm rc://grid.uio.no/lc=Collection,rc=Catalog/badfile#\\
\end{verbatim}

@@

\index{arcacl}\index{commands:arcacl}This command retrieves or modifies
access control information associated with a stored object if service
supports GridSite GACL language~\cite{gacl} for access control.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcacl [options] get$|$put $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
    \texttt{-d, -debug} & \textit{debuglevel} &debug level: 0 = some, 1 = more, 2 = a lot \\
    \texttt{-v} && print version information\\
    \texttt{-h} && short help\\
   Arguments:&&\\
    \texttt{get} &\textit{URL}& get Grid ACL for the object\\
    \texttt{put} &\textit{URL}& set Grid ACL for the object\\
    \texttt{URL} && object URL; curently only gsiftp and sse URLs are supported\\
\end{longtable}

ACL document (an XML file) is printed to standard output when
\texttt{get} is requested, and is acquired from standard input when
\texttt{set} is specified\footnote{In ARC $\leq$ 0.5.28, \texttt{set}
  shoud be used instead of \texttt{put}}. Usage examples are:
\begin{verbatim}
    ngacl get gsiftp://se1.ndgf.csc.fi/ndgf/tutorial/dirname/filename
    ngacl set gsiftp://se1.ndgf.csc.fi/ndgf/tutorial/dirname/filename $<$ myacl
\end{verbatim}

>>>>

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcls [options] $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-l} &  & detailed listing\\
    \texttt{-L} &  & detailed listing including URLs from which file can 
    be downloaded and\\ & & temporary cached locations\\
    \texttt{-m} && display all available metadata\\
    Arguments:&&\\
    \texttt{URL} && file or directory URL\\
\end{longtable}

@@

\begin{verbatim}
    arcls rls://rc.host:38203/logical_file_name
    arcls -l gsiftp://lscf.nbi.dk:2811/jobs/1323842831451666535
    arcls -L srm://grid.uio.no:58000/srm/managerv1/johndoe/log2
\end{verbatim}

@@

The \texttt{arccp} \index{arccp}\index{commands:arccp} is a powerful
tool to copy files over the Grid. It is a part of the A-REX,
but can be used by the User Interface as well.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccp [options] $<$source$>$ $<$destination$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-y} & \textit{cache\_path} & path to local cache (use to put file into cache)\\
    \texttt{-p} && use passive transfer (does not work if secure is on, default if secure is not requested)\\
    \texttt{-n} && do not try to force passive transfer\\
    \texttt{-i} && show progress indicator\\
    \texttt{-u} && use secure transfer (insecure by default)\\
    \texttt{-r} & \textit{recursion\_level} & operate recursively (if possible) up to specified level (0 - no recursion)\\
    \texttt{-R} & \textit{number} & how many times to retry transfer of every file before failing\\
    \texttt{-t} & \textit{time} & timeout in seconds (default 20)\\
    \texttt{-f} && if the destination is an indexing service and not the same as the source and the destination is already registered, then the copy is normally not done. However, if this option is specified the source is assumed to be a replica of the destination created in an uncontrolled way and the copy is done like in case of replication\\
    \texttt{-T} && do not transfer file, just register it - destination must be non-existing meta-url\\
    Arguments:&&\\
    \texttt{source} && source URL\\
    \texttt{destination} && destination URL\\
\end{longtable}

@@

@@

\begin{verbatim}
    arccp gsiftp://lscf.nbi.dk:2811/jobs/1323842831451666535/job.out \
              file:///home/myname/job2.out
    arccp gsiftp://aftpexp.bnl.gov;threads=10/rep/my.file \
              rc://;threads=4@grid.uio.no/lc=Collection,rc=Catalog/zebra4.f
    arccp http://www.nordugrid.org/data/somefile gsiftp://hathi.hep.lu.se/data/
\end{verbatim}

@@

The \texttt{arcrm} \index{arcrm}\index{commands:arcrm}
command allows users to erase files at any location specified by a
valid URL.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcrm [options] $<$source$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-c} & &continue with meta-data even if it failed to delete real file\\
    Arguments:&&\\
    \texttt{source} && source URL\\
\end{longtable}

\begin{framed}
   A convenient use for \texttt{arcrm} is to erase the files in a data
   indexing catalog (RC, RLS or such), as it will not only remove the
   physical instance, but also will clean up the database record.
\end{framed}

@@

\begin{verbatim}
    arcrm rc://grid.uio.no/lc=Collection,rc=Catalog/badfile
\end{verbatim}

@@

\index{arcacl}\index{commands:arcacl}This command retrieves or modifies
access control information associated with a stored object if service
supports GridSite GACL language~\cite{gacl} for access control.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcacl [options] get$|$put $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
    \texttt{-d, -debug} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-v} && print version information\\
    \texttt{-h} && short help\\
   Arguments:&&\\
    \texttt{get} &\textit{URL}& get Grid ACL for the object\\
    \texttt{put} &\textit{URL}& set Grid ACL for the object\\
    \texttt{URL} && object URL; curently only gsiftp and sse URLs are supported\\
\end{longtable}

ACL document (an XML file) is printed to standard output when
\texttt{get} is requested, and is acquired from standard input when
\texttt{set} is specified\footnote{In ARC $\leq$ 0.5.28, \texttt{set}
  shoud be used instead of \texttt{put}}. Usage examples are:
\begin{verbatim}
    arcacl get gsiftp://se1.ndgf.csc.fi/ndgf/tutorial/dirname/filename
    arcacl set gsiftp://se1.ndgf.csc.fi/ndgf/tutorial/dirname/filename $<$ myacl
\end{verbatim}
